With postulate \eqref{mpos:VollstaendigeGenerierendeFunktion} we have layed the groundwork for the practical calculation method. For it to unleash we write the operator $\Ex(\mcL_f)$ in its series expansion by assumption of convergence to 
\[
    Z_{z,R_\omega}[J] = \text{Ex}_{\mcL_f}\nsqbra{Z_{z,R_\omega}^{(0)}}[J] = \sum_{n\in\N} \frac{1}{n!}\cdot\mcL_f^n(Z_{z,R_\omega}^{(0)})[J].
\]
\input{../journal/Tage/2024-05-13/IntegralTransformation.tex}
\input{../journal/Boxen/Korollar/GeneratingFunctionBasis.tex}
% \input{../journal/Tage/2024-05-13/DefinitionFourierLagrange.tex}
With the free theory under Fourier transformation explicitly handled, the two interactive summands now include the two newly introduced vertices $V$ and $\mu_z$. 
The construction of $\text{Ex}$ however remains similar in the Fourier image. 
With this and \cite{mth:vogel} we therefore find:\footnote{The integration domain of the second summand is given by the hyperplane introduced due to the limitation $\drho_{R_\omega}(-(p_1 + p_2 + p_3))$. We assume this to be convered in the measure $\overline\mu_{\overline{\text{III}}}$ and do not discuss it explicitly, since for the one loop order the corresponding Lagrangian integral $\mcL_{f,\overline{\text{III}},\mcF}$ vanishes.}
\begin{align*}
    \mcL_{f,\overline{\text{II}},\mcF} &:= \int_{(\R^d)^2}\mu_z(p)\cdot\bbbra{\frac{\delta}{\delta J(-p_1)}\circ\frac{\delta}{\delta J(-p_1-p_2)}}(\cdot)\;\overline\mu_{\overline{\text{II}}}(dp), \\
    \mcL_{f,\overline{\text{III}},\mcF} &:= \underset{\drho_{134}(\R^d)}{\iiint} V_z(p_3,-p_2)\cdot\bbbra{\frac{\delta}{\delta J(-p_1)}\circ \frac{\delta}{\delta J(-p_3)}}(\cdot)\;\overline\mu_{\overline{\text{III}}}(dp).
\end{align*}
Notice how we can now connect the generating function to our main object of interest, the resolvent. Since expressed with extrapoladed gaussian density, the resolvent involves a factor $\Phi(x)\cdot\Phi(y)$ combined with the density $\Phi\mapsto \exp(S_{z,R_\omega}[\Phi])$, we can extend the integral using the same field shifting technique to 
\begin{multline}
    \int_{\mcF_{d,N}}\Phi(x)\cdot\Phi(y)\cdot \exp((\text{S}_{z,R_\omega}\Phi)[J])\;\uplambda(d\Phi) \\
    = \int_{\mcF_{d,N}}\bbbra{\frac{\delta}{\delta J(-x)}\circ\frac{\delta}{\delta J(-y)}}\cdot{\exp}\bbra{(\text{S}_{z,R_\omega}\Phi)[J]}\;\uplambda(d\Phi).
    \label{eq:GeneratedSecondMomentIntegral}
\end{multline}
The exponential now exactly represents the generating function $Z_{z,R_\omega}[J]$, such that the second moment against gaussian measure can be derived using two functional derivatives.


\subsubchapter{Theoretical Application of the Propagator Representation}
\input{../journal/Tage/2024-05-13/Application-I.tex}
\input{../journal/Boxen/Lemma/VanishingThirdDerivative.tex}
\noindent With the lemma we can safely assume that the first approximation order vanishes for $J = 0$ and therefore the second order is the first non-vanishing term in our approximation. This behaviour in uneven moments can be observed in a generalizing manner: For so called \emph{centeralized gaussian vectors} $X$ the following theorem of Isserlis/Wick holds.
\input{../journal/Boxen/Satz/IsserlisTheorem.tex}
From the theorem it directly follows that for $N\in\textit{uneven}$ we have an empty sum over $P_N^2$ and therefore the expectation value vanishes. We have to consider that Isserlis' theorem is only applicable for \emph{normally distributed} random variables!



\subsubchapter{Visualization: Calculation of one One-Loop Correction Integral}
\label{subsubchapter:VisualizationOneLoop}
\input{../journal/Tage/2024-05-13/OneLoopCalc.tex}
