


% Ich möchte diese Arbeit meiner Studienzeit in Konstanz widmen und allen Erfahrungen, welche ich in jenem Abschnitt meines Lebens habe sammeln dürfen. Besonders danken möchte ich meinen Eltern und meiner Schwester für ihre Unterstützung und ihren Beistand, sowie Arto Steffan und meiner Freundin Artemis für ihre Freundschaft, Hilfe und Motivation.
This thesis is dedicated to my time in Konstanz and all the experiences I have been able to gather during that period of my life. \\

Some sections of this thesis may appear lengthy and have a sticky feel to them. This is due to the amount of work I put into disassembling what was already constructed by experts in this field who are highly skilled physicists and mathematicians. It became a huge challenge for me at some points and I cannot wait to be as fluent as many authors of the papers and books I have read appear to be. But for now I have to try to do a detailed analysis of every component to thoroughly convince myself of physical understanding and to feel the fresh breeze of founded research. \\

Without the technology I am able to savour, the time of writing would have been much more of a struggle. Open sourced tools like vim and \LaTeX\, Julia and Zathura made my days a breeze and joy. And this is what I adore about the world, the human being and spirit; Its ability to create greatness and share it with everyone. \\

This also is what each and every professor and teacher did for me, beginning in the first semester with lectures such as \emph{Analysis 1} with professor Junk and \emph{Lineare Algebra 1} with professor Schweighofer, whose value only later on became clear to me. There were so many other valuable lectures and courses I have been able to attend, I especially think of the \emph{mathematische Grundlagen der Quantenmechanik} by professor Denk, or follow along, I think of the \emph{Theorie und Numerik partieller Differentialgleichungen} by professor Junk and Gmeineder. As a student of physics I naturally also attended great and demanding classes in IK, where I learned from professor Fuchs whose team build the foundation of this thesis, mainly taught to me by their member Florian Vogel. Despite the challenges those classes have brought to me, I am grateful that I had the opportunity to attend and learn from them. They greatly shaped my way of thinking and understanding of everything surrounding me. \\

But now I wish to make place for some of the most thoughtful, inspiring and loving people I have met during my studies. 

Thank you David for the best times I have had during our studys of physics in Constance. I will never forget the walks up and down the stairs at university, the coffees we did not have in class, the cakes we took to tutoriums and the countless hours we invested into our studies. By heart I remember the times at the balcony drinking whine and thinking about tomorrows submissions. You made the studies much more of an ease and I am truly grateful for your friendship.  

Thank you Kai for inspiring me. For inspiring me to see beyond, to think the new and to embrace the unknown. I would never have started Linux, never have thought of so many ideas and never have enjoyed mathematics the way I do without you in my life. 

To Arto, who brought new warmth into my life, who challenged and changed the way I think and act. Who taught and brought me culture of france, art and joy, espaecially in times of the \emph{Franzosen-Action}. And you wondered beneath the stars, what value our friendship would have.. you are the most valuable friend I have. This chapter really is .. \emph{powered by bro}.

And to you \textgreek{Άρτεμις}. I was not prepared to meet you, and yet the subway of HD took off. I still see you standing beneath the public library with a giant hat, a big smile and glowing eyes. During our time you truly made me grow and supported me with all your heart. Without you, life would have been so much of a different story. \textgreek{Σ'αγαπώ αγάπη μου}. \\


Whereas each of you has been by my side physically, I would have never been able to experience this time without my family back at my hometown in Nordenham. You helped me decisively to get through the hard times I espaecially faced during the first year, were with me when things did not work out and helped me regain my confidence in what is to come. I remember the countless evenings we ate together digitally and all the memories created when you visited me in Konstanz, Papa. To this day I enjoy writing to you at the start and very end of every day, Mama. There are virtually no words that could describe what I feel for you. And to my sister, I am so proud of you and so very glad to be on your side. \\

\textit{As I am sitting here by myself, writing the last paragraphs, a truely, truely dense tear runs down my cheek. Without the miracle of you all I would have never loved and enjoyed life as much as I did.}

\begin{center}
    \slshape
    \enquote{Don't hide away - come out and play.}
\end{center}

\vspace{2cm}
\noindent Tom Folgmann\\
\noindent Konstanz, 26.02.2024 and July 2024
